\begin{thebibliography}{99}

\bibitem{A-B} W. Arendt and C. J. K. Batty, Tauberian theorems and stability of one-parameter semigroups, \textit{Trans. Amer. Math. Soc.} 306, (1988) pp. 837--852.
\bibitem{AD} G. Avalos and M. Dvorak A new maximality argument for a coupled fluid-structure interaction with implications for a divergence-free finite element method, \textit{Applicationes Mathematicae,} Vol. 35 (3), (2008), 259-280 

\bibitem{Av} G. Avalos; The strong stability and instability of a fluid-structure semigroup, \textit{Appl, Math. Optim.} (55) (2007), pp. 163-184.

\bibitem{GR} G. Avalos and R. Triggiani; Boundary feedback stabilization of a coupled parabolic-hyperbolic Stokes-Lam-e PDE system, \textit{Journal of Evolution Equations} (9) (2009), pp. 341-370.

\bibitem{av-trig} G. Avalos and R. Triggiani, The Coupled PDE System Arising in Fluid-Structure Interaction, Part I: Explicit Semigroup Generator and its Spectral Properties, \textit{Contemporary Mathematics}, Volume 440, (2007), pp. 15-54.

\bibitem{AvalosLasieckaTriggiani16}
George Avalos, Irena Lasiecka, and Roberto Triggiani.
\newblock Heat-wave interaction in 2--3 dimensions: optimal rational decay
  rate.
\newblock {\em J. Math. Anal. Appl.}, 437(2):782--815, 2016.

\bibitem{AvalosTriggiani09} G. Avalos and R. Triggiani.
\newblock Semigroup well-posedness in the energy space of a
  parabolic-hyperbolic coupled {S}tokes-{L}am\'{e} {PDE} system of
  fluid-structure interaction.
\newblock {\em Discrete Contin. Dyn. Syst. Ser. S}, 2(3): (2009), pp. 417--447.

%\bibitem{AvalosTriggiani2}
%George Avalos and Roberto Triggiani.
%\newblock Rational decay rates for a {PDE} heat-structure interaction: a
 % frequency domain approach.
%\newblock {\em Evol. Equ. Control Theory}, 2(2):233--253, 2013.

\bibitem{AGM} G. Avalos, P. G. Geredeli, B. Muha; \textquotedblleft
Wellposedness, Spectral Analysis and Asymptotic Stability of a Multilayered
Heat-Wave-Wave System \textquotedblright, \emph{Journal of Differential Equations} 269 (2020), pp. 7129-7156.

\bibitem{AA} G. Avalos, P. G. Geredeli; \textquotedblleft
A Resolvent Criterion Approach to Strong Decay of a Multilayered Lamé-Heat System\textquotedblright, \emph{Applicable Analysis,}  https://doi.org/10.1080/00036811.2021.1954165  (2021).

\bibitem{RD} G. Avalos, P. G. Geredeli and B. Muha; Rational Decay of A Multilayered Structure-Fluid PDE System,\textit{ Journal of Mathematical Analysis and Applications 514 (2),\\ https://doi.org/10.1016/j.jmaa.2022.126284} (2022)

\bibitem{Barbu} V. Barbu, Z. Grujić, I. Lasiecka and A. Tuffaha, "Weak and strong solutions in nonlinear fluid-structure interactions", \textit{Contemporary Mathematics} 440: Fluids and Waves, American Mathematical Society, Providence Rhode Island (2007), pp. 55-82.


%\bibitem{Batty19}
%Charles Batty, Lassi Paunonen, and David Seifert.
%\newblock Optimal energy decay for the wave-heat system on a rectangular
%  domain.
%\newblock {\em SIAM J. Math. Anal.}, 51(2):808--819, 2019.

\bibitem{ap-1} Y. Bazilevs, M-C. Hsu, Y. Zhang, W. Wang, T. Kvamsdal, S. Hentschel, J. Isaksen; \textquotedblleft Computational fluid-structure interaction: methods and application to cerebral aneurysms.\textquotedblright , \emph{Biomech Model Machanobiol} 9 (2010), pp. 481-498.

\bibitem{BL} A. Benadallah, I. Lasiecka; Exponential Decay Rates for a Full von Karman System of Dynamic Thermoelasticity, \textit{Journal of Differential Equations} 160 (2000), pp. 51-93. 

\bibitem{bench} C.D. Benchimol; A note on weak stability of contraction semigroups, \textit{SIAM J. Control and Optimization,} Vol. 16 (3), May 1978, pp. 373-379


\bibitem{FSIforBIO}
T. Bodnar, G.~P. Galdi, and S. Necasova, editors.
\newblock {\em Fluid-Structure Interaction and Biomedical Applications}.
\newblock Birkh{\"a}user/Springer, Basel, 2014.

\bibitem{BF} F. Brezzi and M. Fortin; (1991) \textit{Mixed and Hybrid Finite Element Methods,} Springer-Verlag Newyork Inc

\bibitem{multi-layered}
M.~Bukac, S.~Canic, and B.~Muha.
\newblock A partitioned scheme for fluid-composite structure interaction
  problems.
\newblock {\em Journal of Computational Physics}, 281(0): (2015) pp. 493-517.

\bibitem{buk} M. Bukac, S. Canic, B. Muha; \textquotedblleft A nonlinear fluid-structure interaction problem in compliant arteries treated with vascular stents,\textquotedblright \emph{Applied Mathematics and Optimization,} 73 (3), (2016), pp. 433-473.

%\bibitem{bodnar2017particles}
%Tom{\'a}{\v{s}} Bodn{\'a}r, Giovanni~P Galdi, and {\v{S}}{\'a}rka
 % Ne{\v{c}}asov{\'a}.
%\newblock {\em Particles in Flows}.
%\newblock Springer, 2017.


%\bibitem{SunnyStentsSIAM}
%S~{\v C}ani{\' c}.
%\newblock New mathematics for next-generation stent design.
%\newblock {\em SIAM News, April 2019}.

\bibitem{Chambolle} A. Chambolle, B. Desjardins, M.J. Esteban and C. Grandmont, Existence of weak solutions for the unsteady interaction of a viscous fluid with an elastic plate, \textit{J. Math. Fluid Mech }7, no. 3, (2005), pp. 368-404.
 

\bibitem{chen} G. Chen, A note on the boundary stabilization of the wave equation, \textit{SIAM J. Control Optim.} 19: 106--113, 1981.

\bibitem{ciarlet}
Philippe~G. Ciarlet.
\newblock {\em Mathematical elasticity. {V}ol. {I}}: Three-Dimensional Elasticity \newblock North-Holland Publishing Co., Amsterdam, 1988.


\bibitem{ciarlet1} P. G. Ciarlet, \textit{Numerical Analysis of the Finite
Element Method}, \textit{S\'{e}minaire de Math\'{e}matique Sup\'{e}rieures},
Les Presses de L'Universit\'{e} de Montr\'{e}al (1976).

\bibitem{Coutand} D. Coutand and S. Shkoller, ``Motion of an elastic solid inside an incompressible viscous fluid’’, \textit{Arch. Ration. Mech. Anal.} 176 (2005), pp. 25-102.
 
\bibitem{Ger} Geredeli, P.G. An inf-sup approach to $C_0$-semigroup generation for an interactive composite structure-Stokes PDE dynamics. J. Evol. Equ. 24, 50 (2024). https://doi.org/10.1007/s00028-024-00978-3

\bibitem{Ger2} Pelin G. Geredeli, Spectral analysis and asymptotic decay of the solutions to multilayered structure-Stokes fluid interaction PDE system,
Journal of Differential Equations, Volume 427, 2025, Pages 1-25, ISSN 0022-0396, https://doi.org/10.1016/j.jde.2025.01.080.
 
\bibitem{Du} Q. Du, M. D. Gunzburger, L. S. Hou and J. Lee, "Analysis of a linear fluid-structure interaction problem", \textit{Discrete and Continuous Dynamical Systems}, Volume 9, No. 3 (May 2003), pp. 633-650.

\bibitem{uniform} George Avalos, Pelin G. Geredeli, Uniform stability for solutions of a structural acoustics PDE model with no added dissipative feedback, Math. Methods Appl. Sci. 39 (18) (2016) 5497-5512


%\bibitem{GazzolaReview}
%Filippo~Gazzola Denis~Bonheure and Gianmarco Sperone.
%\newblock Eight(y) mathematical questions on fluids and structures.
%\newblock {\em preprint, http://www1.mate.polimi.it/~gazzola/turbulence.pdf}.

%\bibitem{Dowell15}
%Earl~H. Dowell.
%\newblock {\em A modern course in aeroelasticity}, volume 217 of {\em Solid
  %Mechanics and its Applications}.
%\newblock Springer, Cham, enlarged edition, 2015.

%\bibitem{Duyckaerts}
%Thomas Duyckaerts.
%\newblock Optimal decay rates of the energy of a hyperbolic-parabolic system
  %coupled by an interface.
%\newblock {\em Asymptot. Anal.}, 51(1):17--45, 2007.

\bibitem{F} B. Friedman, Principles and Techniques of Applied Mathematics, Dover Publications, Inc., New York, 1990.

\bibitem{GV} P. Grisvard, Elliptic Problems in Nonsmooth Domains, Pitman Publishing Inc., Boston  1985.

%\bibitem{Grisvard2} P. Grisvard, \textit{Singularities in Boundary Value
%Problems, Research Notes in Applied Mathematics 22}, Springer-Verlag, New
%York (1992).

%\bibitem{huang} Huang, F.L. Characteristic conditions for exponential
%stability of linear dynamical systems in Hilbert spaces, \emph{Ann. Differ.
%Equ.}, 1(1), pp. 43-53 (1985).

%\bibitem{Fathallah}
%Ines~Kamoun Fathallah.
%\newblock Logarithmic decay of the energy for an hyperbolic-parabolic coupled
  %system.
%\newblock {\em ESAIM Control Optim. Calc. Var.}, 17(3):801--835, 2011.

%\bibitem{HansenZuazua}
%Scott Hansen and Enrique Zuazua.
%\newblock Exact controllability and stabilization of a vibrating string with an
  %interior point mass.
%\newblock {\em SIAM J. Control Optim.}, 33(5):1357--1391, 1995.

\bibitem{horn} M. A. Horn; Implications of Sharp Trace Regularity Results on Boundary Stabilization of the System of Linear Elasticity, \textit{Journal of Mathematical Analysis and Applications} 223, (1998), pp. 126-150.

\bibitem{hsu} M-C. Hsu, Y. Bazilevs;  \textquotedblleft Blood vessel tissue prestress modeling for vascular fluid–structure interaction simulation\textquotedblright  \emph{Finite Elements in Analysis and Design,} 47, (2011), pp. 593-599.

\bibitem{kesavan} S. Kesavan, Topics in Functional Analysis and Applications, New Age International Limited Publishers, New Delhi (1989).

\bibitem{pazy} Amon Pazy, Semigroups of linear operators and applications to partial differential equations, Vol. 44, Springer Science \& Business Media (2012).

\bibitem{krey} Erwin Kreyszig, Introductory functional analysis with applications, John Wiley \& Sons (1991).

\bibitem{KochZauzua} H. Koch and E. Zuazua.
\newblock A hybrid system of {PDE}'s arising in multi-structure interaction:
  coupling of wave equations in {$n$} and {$n-1$} space dimensions.
\newblock In {\em Recent trends in partial differential equations}, volume 409
  of {\em Contemp. Math.}, pages 55--77. Amer. Math. Soc., Providence, RI,
  2006.

\bibitem{lions1969quelques}
Jacques-Louis and Lions.
\newblock {\em Quelques m{\'e}thodes de r{\'e}solution des problemes aux
  limites non lin{\'e}aires}, volume~31.
\newblock Dunod Paris, 1969.

%\bibitem{MTEFSI}
%Barbara Kaltenbacher, Igor Kukavica, Irena Lasiecka, Roberto Triggiani, Amjad
  %Tuffaha, and Justin~T. Webster.
%\newblock {\em Mathematical theory of evolutionary fluid-flow structure
  %interactions}, volume~48 of {\em Oberwolfach Seminars}.
%\newblock Birkh\"{a}user/Springer, Cham, 2018.
%\newblock Lecture notes from Oberwolfach seminars, November 20--26, 2016.



%\bibitem{LescarretZuazua15}
%Vincent Lescarret and Enrique Zuazua.
%\newblock Numerical approximation schemes for multi-dimensional wave equations
  %in asymmetric spaces.
%\newblock {\em Math. Comp.}, 84(291):119--152, 2015.

%\bibitem{L-P} Y.I. Lyubich and V.Q. Phong, \textquotedblleft Asymptotic
%stability of linear differential equations in Banach
%Spaces\textquotedblright , Studia Matematica, LXXXVII (1988), pp. 37-42.

\bibitem{mclean} W. McLean, \textit{Strongly Elliptic Systems and Boundary
Integral Equations}, Cambridge University Press, NewYork (2000).

\bibitem{BorisSimplifiedFSI}
B. Muha.
\newblock A note on optimal regularity and regularizing effects of point mass
  coupling for a heat-wave system.
\newblock {\em Journal of Mathematical Analysis and Applications}, 425 (2), 2015, pp. 1134-1147.

\bibitem{SunBorMulti}
B. Muha and S. {\v{C}}ani{\'c}.
\newblock Existence of a solution to a fluid--multi-layered-structure
  interaction problem.
\newblock {\em J. Differential Equations}, 256(2), (2014), pp. 658--706.

\bibitem{Necas}  J. Nečas, Direct Methods in the Theory of Elliptic Equations, Springer, New York, 2012 (translated by Gerard Tronel and
Alois Kufner).

\bibitem{RauchZhangZuazua}
J. Rauch, X.~Zhang, and E. Zuazua.
\newblock Polynomial decay for a hyperbolic-parabolic coupled system.
\newblock {\em J. Math. Pures Appl. (9)}, 84(4), (2005), pp. 407-470.

%\bibitem{RichterBook}
%Thomas Richter.
%\newblock {\em Fluid-structure interactions}, volume 118 of {\em Lecture Notes
  %in Computational Science and Engineering}.
%\newblock Springer, Cham, 2017.
%\newblock Models, analysis and finite elements.

\bibitem{temam} R. Temam; \emph{Navier Stokes Equations, Theory and
Numerical Analysis}, AMS Chelsea Publishing, Providence, R.I (2001).

\bibitem{trigg} R. Triggiani, Wave equation on a bounded domain with boundary dissipation: an operator approach, \textit{J. Math. Anal. Appl.} 137: 438-461, 1989.

\bibitem{ZhangZuazuaARMA07}
Xu~Zhang and Enrique Zuazua.
\newblock Long-time behavior of a coupled heat-wave system arising in
  fluid-structure interaction.
\newblock {\em Arch. Ration. Mech. Anal.}, 184(1):49--120, 2007.

\bibitem{tomilov} Y. Tomilov, A resolvent approach to stability of operator semigroups, \emph{J. Operator Theory,} 46,(2001), pp. 63--98.

\bibitem{micuzuazua} S. Micu and E. Zuazua, “Boundary controllability of a linear hybrid system arising in the control of noise ”, SIAM J. Control Optim. , 35(1997), no.5, 1614-1637.


\end{thebibliography}